MLH1 Results Outline

### 2020-03-06 doc/Results.rmd
looking at gamma interference results

load(file="~./MLH1repo/data/CleanBivData_19.2.20.RData")

@@

>>>>

load(file="~./MLH1repo/data/CleanBivData_6.3.20.RData")

@@

```{r Q1.IFD_gamma, echo=FALSE}
library(EnvStats)
#cleanCurated_BivData

#all.female.multi <- (cleanCurated_BivData %>% filter(sex == "female") %>% filter(hand.foci.count > 1) %>%
#                       filter( !is.na( IFD1_ABS) ))  #$IFD1_ABS

#this MELT BIVDATA should be good to go
MELT.IFD.BIVDATA <- melt(cleanCurated_BivData[,c("fileName", "chromosomeLength","centromere_ABS_Position", "centromere_PER_Position",
                            "Obj.ID","hand.foci.count",
                            "mouse","category","strain", "sex", "Rec.group",
                            "IFD1_ABS","IFD2_ABS","IFD3_ABS")],

             id=c("fileName", "chromosomeLength","centromere_ABS_Position", "centromere_PER_Position",
                            "Obj.ID","hand.foci.count",
                            "mouse","category","strain", "sex", "Rec.group"))
#rename the cols and clean up
MELT.IFD.BIVDATA <- MELT.IFD.BIVDATA[(!is.na(MELT.IFD.BIVDATA$value)),]

colnames(MELT.IFD.BIVDATA) <- c("fileName", "chromosomeLength","centromere_ABS_Position", "centromere_PER_Position",
                            "Obj.ID","hand.foci.count",
                            "mouse","category","strain", "sex", "Rec.group", 
                               "whichIFD", "IFDval")

MELT.IFD.BIVDATA$Nrm.IFD <- MELT.IFD.BIVDATA$IFDval / MELT.IFD.BIVDATA$chromosomeLength

#START isolating all the types of IFDs

#all.female.multi$mycol <- apply(all.female.multi[,c('IFD1_ABS','IFD2_ABS','IFD3_ABS')], 1, function(x) x[!is.na(x)][1])

all.female.IFDs <- MELT.IFD.BIVDATA %>% filter(sex == "female")#1697

all.male.IFDs <- MELT.IFD.BIVDATA %>% filter(sex == "male")#1392

#gamma fits
FULL.female.gamma <- egamma( all.female.IFDs$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3.8

#gamma fits
FULL.male.gamma <- egamma( all.male.IFDs$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#shape  5.4

#male, stronger interference

WSB.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "WSB")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3.1, 3.73 (raw, PER) (n=252)

WSB.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3.6, 5.10 (raw, PER) (n=186)
#try the short and long bivalents dataset

WSB.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "WSB") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3, 3.237 (raw, PER) (n=60)

#gamma fits
WSB.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "WSB")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3.5,  5.1 (raw, PER) (n= 109)

WSB.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3.9, 3.9 (raw, PER)  (n=107)
#there are 0 3CO and 2  4CO bivalents -- this causes a greater difference in the PER based value

```{r gamma.IFD, echo=FALSE}

female.gamma <- egamma( (all.female.IFDs )$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

f2CO.female.gamma <- egamma( (all.female.IFDs  %>% filter(hand.foci.count == 2)  )$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

f3CO.female.gamma <- egamma( (all.female.IFDs %>%  filter(hand.foci.count == 3)  )$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

f4CO.female.gamma <- egamma( (all.female.IFDs %>%  filter(hand.foci.count == 4)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###

PWD.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "PWD")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3.8, 4.844 (raw, nrm)  (n = 357)
PWD.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "PWD") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3.8, 6.746 (raw, nrm) (n = 285)
PWD.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "PWD") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#3, 3.628 (n = 72)

KAZ.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "KAZ")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#

KAZ.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "KAZ") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#

KAZ.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "KAZ") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
#####
SKIVE.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "SKIVE")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
SKIVE.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "SKIVE") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
SKIVE.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "SKIVE") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
##
MSM.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "MSM")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
MSM.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "MSM") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
MSM.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "MSM") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

MSM.4CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "MSM") %>% filter(hand.foci.count == 4)  )$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

######
G.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "G")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
G.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "G") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
G.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "G") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

G.4CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "G") %>% filter(hand.foci.count == 4)  )$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

######
LEW.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "LEW")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
LEW.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "LEW") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
LEW.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "LEW") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

LEW.4CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "LEW") %>% filter(hand.foci.count == 4)  )$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
######
WSB.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "WSB")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
WSB.2CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
WSB.3CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "WSB") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

WSB.4CO.female.gamma <- egamma( (all.female.IFDs %>% filter(strain == "WSB") %>% filter(hand.foci.count == 4)  )$IFDval, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

```{r Q1.male.IFD, echo=FALSE}

#gamma fits
male.gamma <- egamma( (all.male.IFDs )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

m2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

m3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE,         ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###
#gamma fits
PWD.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "PWD")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#8.1, 11.74 (n=318) (lots of variation when I apply sample size of 18)

PWD.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "PWD") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#10.3, 16.962, (n=300)

PWD.3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "PWD") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#2.9, 3.4, (n=18)

####
KAZ.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "KAZ")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
KAZ.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "KAZ") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
KAZ.3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "KAZ") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###
SKIVE.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "SKIVE")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
SKIVE.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "SKIVE") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
SKIVE.3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "SKIVE") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###
MSM.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "MSM")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
MSM.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "MSM") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE,     ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
MSM.3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "MSM") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###
MOLF.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "MOLF")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
MOLF.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "MOLF") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
MOLF.3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "MOLF") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###
G.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "G")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
G.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "G") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
G.3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "G") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###
LEW.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "LEW")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
LEW.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "LEW") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
LEW.3CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "LEW") %>% filter(hand.foci.count == 3)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)

###
WSB.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "WSB")  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
#
WSB.2CO.male.gamma <- egamma( (all.male.IFDs %>% filter(strain == "WSB") %>% filter(hand.foci.count == 2)  )$Nrm.IFD, method = "mle", ci = TRUE, 
                            ci.type = "two-sided", ci.method = "normal.approx", 
                            normal.approx.transform = "kulkarni.powar", conf.level = 0.95)
